Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-08-04 paper/paper-nature-revised.tex
small changes, updated bib

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 26, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, frame hidden, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard\textsuperscript{1}, plays a fundamental role in capturing the
history of political proceedings and facilitating the exploration of
valuable research questions. Originating in the British parliament, the
production of Hansard became tradition in many other Commonwealth
countries, such as Canada and Australia\textsuperscript{2}. Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to September 2022,
containing details on everything said in parliament in a form that can
be readily used by researchers. With the development of tools for
large-scale text analysis, this database will serve as a resource for
understanding political behaviour in Australia over time.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. And finally, there has been examination of
speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, the Hansard has been used to
investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark\textsuperscript{13}.
Question Time data from Hansard transcripts during February and March of
2003 has been used to investigate resistance of politicians in answering
questions about Iraq\textsuperscript{14}. Hansard has also been used to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials\textsuperscript{15}. Finally, a
dataset of the Australian Hansard has been constructed and then used to
analyze the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament\textsuperscript{16}. This was created
with the static PDF versions of Hansard, using OCR to digitize these
files into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages\textsuperscript{17,18}. Focusing on one transcript also allowed
us to ensure that all key components of the transcript were parsed and
captured in as much detail as possible. The typical form of a Hansard
XML transcript is summarized in the nested list below. This provides an
overview, but does not contain every possible nested element that may be
found in a Hansard XML.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child nodes,
where the first child node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the MP whose turn it is to speak and the time of their
first statement. Unsurprisingly, speeches rarely go uninterrupted in
parliamentary debate settings --- they are often composed of a series of
interjections and continuations. These statements are categorized under
different sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will \protect\hyperlink{sec-qa}{follow}.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{19}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in the Interjections
\protect\hyperlink{sec-interject}{section} to follow.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted. These became apparent as we ran
our script on XML files from earlier sitting days. Some changes are as
subtle as a differently named child node, while others are as extensive
as a completely different nesting structure. Smaller changes were
accounted for as we became aware of them, and embedded into the code in
a way that would not cause issues for parsing more current Hansards with
subtle differences in formatting. However, as mentioned, more
significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards.
Further not every sitting day contains every possible XML element. For
example, some days did not have
\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse exists in the file.

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day this first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we prioritized cleaning and finalizing what we had been able
to parse. As such we continued building our script, fixing any problems
we noticed in the resulting datasets such as excess whitespace or
spacing issues, and splitting up any additional sections of the parsed
text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in the subsequent Stage
Directions \protect\hyperlink{sec-stage}{section}. After completing our
first script, it was formatted as a function which takes a single file
name argument and produces one CSV file containing data on all
proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the
1998-2022 time frame of Hansard documents. Two main factors motivated us
to create four scripts as opposed to just one, the first being
structural variation in XML over time, and the second being improved
computational efficiency with separate scripts. While all four scripts
use the same general approach to parsing described in the Overview
\protect\hyperlink{sec-overview}{section} and produce the same CSV
structure, the first and second scripts use a different method of data
processing than the third and fourth scripts.

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{20}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

As mentioned in the Script Differences
\protect\hyperlink{sec-diff}{section}, more recent years of Hansard XMLs
contain a series of child nodes which exist to capture the structure of
interruptions in that speech. Figure~\ref{fig-xml2} provides an example
of this, where the speech was interrupted by a comment from the Deputy
Speaker, and then the MP continued their speech. Looking at the element
names highlighted in blue, these child nodes do not contain the actual
text for the interjection or continuation --- this text is embedded
within the speech above it. However, as shown by the content highlighted
in pink in Figure~\ref{fig-xml2}, we were able to extract useful details
on the individual interjecting which we could use later. Making use of
this structure, we extracted names and information of all individuals
that were categorized within the XML as interjections. We stored this as
a dataframe called \texttt{"interject"}. We decided not to include this
data in our final database, as it is embedded in our resulting datasets
which have a flag for interjections.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table\textsuperscript{11}.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
in the Script Differences \protect\hyperlink{sec-diff}{section}, we used
string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml2},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed. In particular, while most
statements were categorized in their own child node and hence captured
through pattern-based separation, some were not individually
categorized, and had to be split manually in this step.

@@

In the Hansard XML files, divisions data are structured outside of the
\texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in the Script Differences
\protect\hyperlink{sec-diff}{section} naturally allowed for much of the
divisions data to be added to our resulting files for 1998 to March
2011, however the parsing scripts used for May 2011 to September 2022
Hansard did not. To supplement our database and in an effort to fill
this divisions data gap, we created an additional file containing all
divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any timestamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}division\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.

@@

Our database is available in both CSV and parquet formats. Both CSV and
parquet are open standards. We provide both because while CSVs are
commonly used and can be manually inspected, parquet files are typically
smaller and preserve class. Our database covers all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022 where
an XML transcript is available, so there are 1,532 individual sitting
day files for each format. Additionally, there is a single corpus file
in both CSV and parquet forms containing the data from all sitting days,
with a date variable added to allow for distinction and filtering of
individual sitting days. There is also a CSV and parquet file containing
all parsed debate topics. All data records are available on the
general-purpose repository Zenodo, at
\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{21}. For
each Hansard data file, that is, the corpus and the individual sitting
day files, each row contains an individual statement, with details on
the individual speaking. For general statements transcribed as made by
``Honourable members'' for example, these variables cannot be specified.
Table~\ref{tbl-vars} provides an overview of each variable found in the
Hansard data files in the database.

@@

We then computed the total number of speeches made in our database by
political party, summarized in Table~\ref{tbl-speeches_by_party}. We
found that the Australian Labor Party made the most speeches overall,
followed by the Liberal Party of Australia, and the National Party of
Australia. These rankings are unsurprising, as those parties are the
three main political parties in the Australian House of
Representatives\textsuperscript{22}.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages\textsuperscript{11,23}. By
including this variable, one can readily integrate our data records with
those available in these two packages. Similarly, we added the
\texttt{partyfacts\_id} variable to our data which allows users to link
our data to external political party data sources with this unique
identifier.

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook\textsuperscript{10}. This will allow
for convenient extraction of further details on each MP in a tidy, ready
to analyze format.

@@

The code written to build this database is available on the GitHub
repository associated with this paper
(https://github.com/lindsaykatz/hansard-proj). All scripts were created
using R software\textsuperscript{24}. The core packages used to develop
these scripts are: the \texttt{XML} package\textsuperscript{17}, the
\texttt{xml2} package\textsuperscript{18}, the \texttt{tidyverse} R
packages\textsuperscript{25}, the \texttt{AustralianPoliticians}
package\textsuperscript{11}, and the \texttt{ausPH}
package\textsuperscript{10}. \texttt{XML} and \texttt{xml2} were used
for parsing the XML documents, \texttt{AustralianPoliticians} and
\texttt{ausPH} were used for cleaning up and filling in MP details in
the datasets, and \texttt{tidyverse} packages were used in all steps,
for tidy wrangling of data.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-citehansard}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Commonwealth of Australia.
\href{https://www.aph.gov.au/Parliamentary_Business/Hansard}{Parliamentary
debates, house of representatives}. (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Vice, J. \& Farrell, S. \emph{The history of hansard}.
(House of Lords Library; House of Lords Hansard, 2017).}

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{August 3, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, enhanced, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard\textsuperscript{1}, plays a fundamental role in capturing the
history of political proceedings and facilitating the exploration of
valuable research questions. Originating in the British parliament, the
production of Hansard became tradition in many other Commonwealth
countries, such as Canada and Australia\textsuperscript{2}. Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from March 1998 to September
2022, containing details on everything said in parliament in a form that
can be readily used by researchers. With the development of tools for
large-scale text analysis, this database will serve as a resource for
understanding political behaviour in Australia over time.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created
(http://historichansard.net/). These data can be navigated by year,
parliament, people, and bills. To make the Australian Parliamentary
Handbook more accessible, an \texttt{R} package which includes data on
all MPs from 1945 to 2019 has been created
(https://github.com/palesl/AustralianHouseOfRepresentatives). Further,
there is the \texttt{AustralianPoliticians} \texttt{R} package, which
contains several datasets related to the political and biographical
information of Australian federal politicians who were active between
1901 and 2021\textsuperscript{9}. And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{10}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, the Hansard has been used to
investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark\textsuperscript{11}.
Question Time data from Hansard transcripts during February and March of
2003 has been used to investigate resistance of politicians in answering
questions about Iraq\textsuperscript{12}. Hansard has also been used to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials\textsuperscript{13}. Finally, a
dataset of the Australian Hansard has been constructed and then used to
analyze the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament\textsuperscript{14}. This was created
with the static PDF versions of Hansard, using OCR to digitize these
files into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

The approach to parsing contents of an XML document depends on its tree
structure. As such, to create this database, we started by looking at a
single Hansard XML transcript from 2019. Doing so enabled us to identify
the various components of interest in the document, and how each one can
be parsed according to its corresponding structural form. Parsing was
performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
packages\textsuperscript{15,16}. Focusing on one transcript also allowed
us to ensure that all key components of the transcript were parsed and
captured in as much detail as possible. The typical form of a Hansard
XML transcript is summarized in the nested list below. This provides an
overview, but does not contain every possible nested element that may be
found in a Hansard XML.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child nodes,
where the first child node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the MP whose turn it is to speak and the time of their
first statement. Unsurprisingly, speeches rarely go uninterrupted in
parliamentary debate settings --- they are often composed of a series of
interjections and continuations. These statements are categorized under
different sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow.

@@

The next step was to further develop our script to produce tidy data
sets\textsuperscript{17}. These contain all parsed text elements, where
each statement is separated onto its own row with details about the MP
who is speaking, and rows are maintained in chronological order. This
first involved correcting the variable classes and adding several
indicator variables to differentiate where statements came from, such as
Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided later.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted. These became apparent as we ran
our script on XML files from earlier sitting days. Some changes are as
subtle as a differently named child node, while others are as extensive
as a different nesting structure. Smaller changes were accounted for as
we became aware of them, and embedded into the code in a way that would
not cause issues for parsing more current Hansards with subtle
differences in formatting. However, as mentioned, more significant
changes in the XML structure of Hansard necessitated the development of
separate scripts as we worked backwards. Further not every sitting day
contains every possible XML element. For example, some days did not have
\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse exists in the file.

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day this first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we prioritized cleaning and finalizing what we had been able
to parse. As such we continued building our script, fixing any problems
we noticed in the resulting datasets such as excess whitespace or
spacing issues, and splitting up any additional sections of the parsed
text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in the Stage Directions
section. After completing our first script, it was formatted as a
function which takes a single file name argument and produces one CSV
file containing data on all proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the
1998-2022 time frame of Hansard documents. Two main factors motivated us
to create four scripts as opposed to just one, the first being
structural variation in XML over time, and the second being improved
computational efficiency with separate scripts. While all four scripts
use the same general approach to parsing described in the Overview
section and produce the same CSV structure, the first and second scripts
use a different method of data processing than the third and fourth
scripts.

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real
time\textsuperscript{18}. Questions without notice are included directly
in the \texttt{"chamber.xscript"} child node, with sub-child nodes
called \texttt{"question"} and \texttt{"answer"} to differentiate the
two. Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

As mentioned earlier, more recent years of Hansard XMLs contain a series
of child nodes which exist to capture the structure of interruptions in
that speech. Figure~\ref{fig-xml2} provides an example of this, where
the speech was interrupted by a comment from the Deputy Speaker, and
then the MP continued their speech. Looking at the element names
highlighted in blue, these child nodes do not contain the actual text
for the interjection or continuation --- this text is embedded within
the speech above it. However, as shown by the content highlighted in
pink in Figure~\ref{fig-xml2}, we were able to extract useful details on
the individual interjecting which we could use later. Making use of this
structure, we extracted names and information of all individuals that
were categorized within the XML as interjections. We stored this as a
dataframe called \texttt{"interject"}. We decided not to include this
data in our final database, as it is embedded in our resulting datasets
which have a flag for interjections.

@@

We then added an order variable to the dataset based on row number, to
keep track of the order in which everything was said. The next step was
to fill the name, name ID, electorate and party variables with the
correct data for each row. We also wanted to add the gender and unique
identifier for each individual as found in the
\texttt{AustralianPoliticians} package. To do so, we created a lookup
table, which contained the unique incomplete form in which the name was
transcribed, and the corresponding full name, name ID, electorate,
party, gender, and unique ID for that individual.
Figure~\ref{fig-lookup} provides an example of this. We used the main
dataset from the \texttt{AustralianPoliticians} package in the creation
of each lookup table\textsuperscript{9}.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
earlier, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml2},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed. In particular, while most
statements were categorized in their own child node and hence captured
through pattern-based separation, some were not individually
categorized, and had to be split manually in this step.

@@

In the Hansard XML files, divisions data are structured outside of the
\texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in the Script Differences section naturally allowed
for much of the divisions data to be added to our resulting files for
1998 to March 2011, however the parsing scripts used for May 2011 to
September 2022 Hansard did not. To supplement our database and in an
effort to fill this divisions data gap, we created an additional file
containing all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any timestamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}division\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.

@@

Our database is available in both CSV and parquet formats. Both CSV and
parquet are open standards. We provide both because while CSVs are
commonly used and can be manually inspected, parquet files are typically
smaller and preserve class. Our database covers all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022 where
an XML transcript is available, so there are 1,532 individual sitting
day files for each format. Additionally, there is a single corpus file
in both CSV and parquet forms containing the data from all sitting days,
with a date variable added to allow for distinction and filtering of
individual sitting days. There is also a CSV and parquet file containing
all parsed debate topics. All data records are available on the
general-purpose repository Zenodo, at
\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{19}. For
each Hansard data file, that is, the corpus and the individual sitting
day files, each row contains an individual statement, with details on
the individual speaking. For general statements transcribed as made by
``Honourable members'' for example, these variables cannot be specified.
Table~\ref{tbl-vars} provides an overview of each variable found in the
Hansard data files in the database.

@@

We then computed the total number of speeches made in our database by
political party, summarized in Table~\ref{tbl-speeches_by_party}. We
found that the Australian Labor Party made the most speeches overall,
followed by the Liberal Party of Australia, and the National Party of
Australia. These rankings are unsurprising, as those parties are the
three main political parties in the Australian House of
Representatives\textsuperscript{20}.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the
\texttt{AustralianPoliticians}\textsuperscript{9} and
\texttt{AustralianElections} R packages
(https://github.com/RohanAlexander/AustralianElections). By including
this variable, one can integrate our data records with those available
in these two packages. Similarly, we added the \texttt{partyfacts\_id}
variable to our data which allows users to link our data to external
political party data sources with this unique identifier.

Further, the \texttt{name.id} variable found in each file is another
unique identifier for each MP. This variable was parsed directly from
the Hansard XML files, and can be found in the Australian Parliamentary
Handbook. As such, our data records can be integrated with those from
the \texttt{ausPH} package which provides datasets for contents of the
Australian Parliamentary Handbook. This will allow for convenient
extraction of further details on each MP in a tidy, ready to analyze
format.

@@

The code written to build this database is available on the GitHub
repository associated with this paper
(https://github.com/lindsaykatz/hansard-proj). All scripts were created
using R software\textsuperscript{21}. The core packages used to develop
these scripts are: the \texttt{XML} package\textsuperscript{15}, the
\texttt{xml2} package\textsuperscript{16}, the \texttt{tidyverse} R
packages\textsuperscript{22}, the \texttt{AustralianPoliticians}
package\textsuperscript{9}, and the \texttt{ausPH} package. \texttt{XML}
and \texttt{xml2} were used for parsing the XML documents,
\texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
up and filling in MP details in the datasets, and \texttt{tidyverse}
packages were used in all steps, for tidy wrangling of data.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-citehansard}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Commonwealth of Australia.
\href{https://www.aph.gov.au/Parliamentary_Business/Hansard}{{Parliamentary
Debates, House of Representatives}}. (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Vice, J. \& Farrell, S. \emph{{The history of Hansard}}.
(House of Lords Library; House of Lords Hansard, 2017).}
